Network Cascades

### 2016-08-26 paper/paper.tex
Add the final two graphs to findings section

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[width=\columnwidth]{img/heterogenity}
  \caption{Effect of heterogenity on cascade size, image from \cite{simplemodel}. The $\phi$ are normally distribute width a standard derivation of $\sigma$.}
  \label{fig:heterogenity}
\end{figure}

Similarly distributed results can be observed in networks that vary in their distribution of $\phi$ and $p_k$, but the exact results differ in quantity. Figure \ref{fig:heterogenity} shows that increasing the variation of thresholds in the network also increases the likelihood of cascades. Using identical, homogenous thresholds for all agents yields the most stable system, while increasing the derivation and giving the nodes differing thresholds consistently decreases this stability, enabling more successful cascades.

\begin{figure}[h!]
  \centering
  \includegraphics[width=\columnwidth]{img/dunnolol}
  \caption{A confusing graph, image from \cite{simplemodel}.}
  \label{fig:heterogenity}
\end{figure}
